---
title: "Interacted model example"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  toc: true
toc_depth: 3
toc_float:
  collapsed: false
smooth_scroll: false
editor_options:
  chunk_output_type: console
---

Simulating and estimating teh interacted model

```{r,message=FALSE,warning=FALSE}
require(rblm)
require(knitr)
#require(kableExtra)
options(knitr.table.format = "html") 
```


# Simulating a data set

The interacted model has the following equations:

$$  y_{it} = a_t(k_{it}) + b_t(k_{it}) \cdot \alpha_i + \epsilon_{it}$$
where in the model we define the average worker quality conditional on a firm type:

$$ \text{Em} =  E[ \alpha_i |k,t=1  ]  $$

and the average wroker quality conditional on a job change:
$$ \text{EEm} =  E[ \alpha_i |k_1{=}k,k_2{=}k',m{=}1  ]  $$


```{r}
set.seed(324313)
model = m2.mini.new(10,serial = F,fixb=T)

# we set the parameters to something simple
model$A1 = seq(0,2,l=model$nf) # setting increasing intercepts
model$B1 = seq(1,2,l=model$nf) # adding complementarity (increasing interactions)
model$Em = seq(0,1,l=model$nf) # adding sorting (mean type of workers is increasing in k)

# we make the model stationary (same in both periods)
model$A2 = model$A1
model$B2 = model$B1

# setting the number of movers and stayers 
model$Ns   = array(300000/model$nf,model$nf)
model$Nm   = 10*toeplitz(ceiling(seq(100,10,l=model$nf)))

# creating a simulated data set
ad =  m2.mini.simulate(model)

# plot firm size distribution
ggplot(ad$sdata[,.N,f1],aes(x=N)) + geom_histogram(binwidth=1) + theme_bw()

```

# Clustering firms 

We start by extracting the measures that will be used to cluster
```{r}
ms    = grouping.getMeasures(ad,"ecdf",Nw=20,y_var = "y1")
# then we group we choose k=10
grps  = grouping.classify.once(ms,k = 10,nstart = 1000,iter.max = 200,step=250)

# finally we append the results to adata
ad   = grouping.append(ad,grps$best_cluster,drop=T)

# we can also check the classification
ggplot(ad$sdata[,.N,list(j1,j1true)],aes(x=j1true,y=j1,size=N)) + geom_point() + theme_bw() +
  scale_x_continuous("true type") + scale_y_continuous("estimated group")
```

In the previous command we tell rblm that we want to use the firm
specific empirical measure "ecdf" with 20 points of supports and that
the dependent variable is "y1". The firm identifier should be "f1".

# Estimating the model 

This is a relatively old code, we will be pushing an update extremely soon!

```{r}
res = m2.mini.estimate(ad$jdata,ad$sdata,model0 = model,method = "fixb")
```

We can show the decompositions next to each other:

```{r}
kable(rbind(model$vdec$stats,res$vdec$stats),digits = 4) 
```


And we can plot the resulting wage, next to the true ones

```{r}
m2.mini.plotw(res)    + ggtitle("Estimated wages")
m2.mini.plotw(model)  + ggtitle("Model wages")
```

## Estimating using quasi-likelihood

This is a new estimator we have been working on.

We start by extracting all necesserary moments for off-line estimation:

```{r}
mstats = ad$jdata[,list(m1=mean(y1),sd1=sd(y1),
                         m2=mean(y2),sd2=sd(y2),
                         v12 = cov(y1,y2),.N),list(j1,j2)]
cstats = ad$sdata[,list(m1=mean(y1),sd1=sd(y1),
                         m2=mean(y2),sd2=sd(y2),
                         v12 = cov(y1,y2),.N),list(j1)]
```

Then we estimate using the quasi-likelihood estimator:
```{r,warning=FALSE,results=FALSE}
res2 = m2.minirc.estimate(cstats,mstats,method = 2)
```

here is the variance decomposition:

```{r}
dd = rbind(model$vdec$stats,res$vdec$stats,res2$vdec$stats)
kable(dd,digits = 4) 
```
