---
title: "Mixture model example"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  toc: true
toc_depth: 3
toc_float:
  collapsed: false
smooth_scroll: false
editor_options:
  chunk_output_type: console
---

Simulating and estimating the mixture model

```{r,message=FALSE,warning=FALSE}
require(rblm)
require(knitr)
options(knitr.table.format = "html") 
```


# Simulating a data set

The interacted model has the following equations:

$$  Pr[ Y_{it} \leq y | k,\ell ] = \Phi( \mu_{k\ell}, \sigma_{k\ell}) $$

```{r}
set.seed(324313)
model = m2.mixt.new(nk=3,nf=5,fixb=T,stationary = T)

# simple complementatiry
model$A1 = seq(0.1,1,l=model$nf) %o% seq(0.1,1,l=model$nk)
model$A2 = model$A1

# small variance
model$S1[] = 0.2
model$S2[] = 0.2

# simple sorting
model$pk0[1,,] = exp(3*model$A1)/rowSums(exp(3*model$A1))

# setting the number of movers and stayers 
model$NNs   = array(300000/model$nf,model$nf)
model$NNm   = model$nf*toeplitz(ceiling(seq(100,10,l=model$nf)))

# creating a simulated data set
ad =  m2.mixt.simulate.sim(model,fsize = 40)

# plot firm size distribution
ggplot(ad$sdata[,.N,f1],aes(x=N)) + geom_histogram(binwidth=1) + theme_bw()

```

# Clustering firms 

We start by extracting the measures that will be used to cluster
```{r}

# constructing the measures, we use empirical CDF at each firm
ms    = grouping.getMeasures(ad,            # the data
                             "ecdf",        # the type of moments to construct at the firm level
                             Nw=10,         # number of point of support to use for the method
                             y_var = "y1")  # variable to use to construct moments

# classify into groups
grps  = grouping.classify.once(ms,                  # input the measures to use
                               k = 5,               # number of groups
                               nstart = 1000,       # number of starting values for kmean
                               iter.max = 200,      # max number of iterations for each kmean
                               step=250)            # how often to show output

# finally we append the results to adata
ad   = grouping.append(ad,grps$best_cluster,drop=T)

# we can also check the classification
ggplot(ad$sdata[,.N,list(j1,j1true)],aes(x=j1true,y=j1,size=N)) + geom_point() + theme_bw() +
  scale_x_continuous("true type") + scale_y_continuous("estimated group")
```

In the previous command we tell rblm that we want to use the firm
specific empirical measure "ecdf" with 20 points of supports and that
the dependent variable is "y1". The firm identifier should be "f1".

# Estimating the model 

```{r}
# we set control parameters for the EM
ctrl  = em.control( nplot=10000,         # how often to plot (either wages, or model versus model0)
                    ncat =2000,          # how often to show step increases (large to keep output small)
                    model0 = model,      # a model to compare estimates too (this is for testing)  
                    fixb=TRUE,           # impose fixed interactions over time
                    tol=1e-7,            # tolerance to stop EM      
                    est_rep=2,           # number of starting values to use (we usually use 50)
                    est_nbest=1,         # how many best liklihood to choose the best connected model from (we usually use 10)
                    sdata_subsample=0.1) # whether to sub-sample the stayers in estimation

res = m2.mixt.estimate.all(sim=ad,         # the data
                           nk=model$nk,    # number of worker types (we use here the same as in simulation)
                           ctrl=ctrl)      # parameters to control the EM
```


# Plotting the results

```{r}
m2.mixt.wplot(res$model$A1)
m2.mixt.wplot(model$A1)
m2.mixt.pplot(res$model$pk0[1,,])
m2.mixt.pplot(model$pk0[1,,])
```

