---
title: "BLM example using simulated data"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  toc: true
toc_depth: 3
toc_float:
  collapsed: false
smooth_scroll: false
editor_options:
  chunk_output_type: console
---

Simulating and estimating teh interacted model

```{r,message=FALSE,warning=FALSE}
require(rblm)
require(knitr)
require(kableExtra)
options(knitr.table.format = "html") 
```

# Simulating a data set

```{r}
set.seed(43243123)
model = m2.mini.new(10,serial = F,fixb=T)
model$Ns   = array(300000/model$nf,model$nf)
model$Nm   = 10*toeplitz(ceiling(seq(100,10,l=model$nf)))
sdata = m2.mini.simulate.stayers(model,model$Ns)
jdata = m2.mini.simulate.movers(model,model$Nm)

# compute decomposition
stayer_share = sum(model$Ns)/(sum(model$Ns)+sum(model$Nm))
model$vdec   = m2.mini.vdec(model,1e6,stayer_share,"y1")

# randomly assign firm IDs
sdata <- sdata[,f1:=paste("F",j1 + model$nf*(sample.int(.N/50,.N,replace=T)-1),sep=""),j1]
sdata <- sdata[,j1b:=j1]
sdata <- sdata[,j1true := j1]
jdata <- jdata[,j1true := j1][,j2true := j2]
jdata <- jdata[,j1c:=j1]
jdata <- jdata[,f1:=sample( unique(sdata[j1b==j1c,f1]) ,.N,replace=T),j1c]
jdata <- jdata[,j2c:=j2]
jdata <- jdata[,f2:=sample( unique(sdata[j1b==j2c,f1])  ,.N,replace=T),j2c]
jdata$j2c=NULL
jdata$j1c=NULL
sdata$j1b=NULL

# combine the movers and stayers, ad stands for all data:
ad = list(sdata=sdata,jdata=jdata)

# plot firm size distribution
ggplot(ad$sdata[,.N,f1],aes(x=N)) + geom_histogram(binwidth=1)

```

# Clustering firms 

We start by extracting the measures that will be used to cluster
```{r}
ms    = grouping.getMeasures(ad,"ecdf",Nw=20,y_var = "y1")
# then we group we choose k=10
grps  = grouping.classify.once(ms,k = 10,nstart = 1000,iter.max = 200,step=250)

# finally we append the results to adata
ad   = grouping.append(ad,grps$best_cluster,drop=T)

# we can also check the classification
ggplot(ad$sdata[,.N,list(j1,j1true)],aes(x=j1true,y=j1,size=N)) + geom_point()
```

In the previous command we tell rblm that we want to use the firm
specific empirical measure "ecdf" with 20 points of supports and that
the dependent variable is "y1". The firm identifier should be "f1".

# Estimating the model 

This is a relatively old code, we will be pushing an update extremely soon!

```{r}
res = m2.mini.estimate(ad$jdata,ad$sdata,model0 = model,method = "fixb")
```

We can show the decompositions next to each other:

```{r}
kable(rbind(model$vdec$stats,res$vdec$stats),digits = 4) %>%
  kable_styling(bootstrap_options = c("striped", "bordered","condensed"), full_width = F)
```


And we can plot the resulting wage

```{r}
m2.mini.plotw(res)
```



# Extract all necesserary moments for off-line estimation

```{r}
mstats = ad$jdata[,list(m1=mean(y1),sd1=sd(y1),
                         m2=mean(y2),sd2=sd(y2),
                         v12 = cov(y1,y2),.N),list(j1,j2)]
cstats = ad$sdata[,list(m1=mean(y1),sd1=sd(y1),
                         m2=mean(y2),sd2=sd(y2),
                         v12 = cov(y1,y2),.N),list(j1)]
```




